A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-10 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
add comment about reco cwp doc
CWP CSBS: fix comment related to AARC project participants

  performance at future facilities, e.g., charged-particle tracking. A
  number of such efforts are already in progress.

@@

The evolution of Authentication and Authorisation is being evaluated in
the recently created WLCG Working Group on Authorisation.
In parallel, HEP is contributing to a wider effort
to document requirements for multiple Research Communities through the
work of FIM4R~\cite{FIM4R}. CERN's participation in the European
Authentication and Authorisation for Research and Collaboration (AARC)
project~\cite{AARC} provides the opportunity to ensure
that any directions chosen are consistent with those taken by the wider
community of research collaborations. The flow of attributes between
federated entities continues to be problematic, disrupting the
authentication flow. Trust between service providers and identity
providers is still evolving, and efforts within the R\&E Federations
Group (REFEDS)~\cite{REFEDS} and the AARC project aim to address the
visibility of both the level of assurance of identities and the security
capability of federation participants (through Sirtfi~\cite{Sirtfi}).

>>>>

  performance at future facilities, most significantly 
  charged-particle tracking. A
  number of efforts in this area are already in progress~\cite{recocwp}.

@@

The evolution of Authentication and Authorisation is being evaluated in
the recently created WLCG Working Group on Authorisation.
In parallel, HEP is contributing to a wider effort
to document requirements for multiple Research Communities through the
work of FIM4R~\cite{FIM4R}. Participation of CERN and a few other major
WLCG sites in the European
Authentication and Authorisation for Research and Collaboration (AARC)
project~\cite{AARC} provides the opportunity to ensure
that any directions chosen are consistent with those taken by the wider
community of research collaborations. The flow of attributes between
federated entities continues to be problematic, disrupting the
authentication flow. Trust between service providers and identity
providers is still evolving, and efforts within the R\&E Federations
Group (REFEDS)~\cite{REFEDS} and the AARC project aim to address the
visibility of both the level of assurance of identities and the security
capability of federation participants (through Sirtfi~\cite{Sirtfi}).
